e9_altsAnalysis

### 2015-10-06 analysis/e9_altsAnalysis.Rmd
alts analysis in R, just reading in data and superficial look at alt sets

```{r}
#library(rjson)
rm(list = ls())
library(jsonlite)
setwd("~/Desktop/Projects/scalar_implicature/")
```

```{r}
d0 = fromJSON(file="alts.json")
names(d0)
scalar_data = c()
for (scalar in names(d0)) {
  for(word in d[[scalar]]) {
    scalar = c(scalar, word)
    print(scalar)
  }
  scalar_data = rbind(scalar_data, scalar)
}
scalar_data
```

```{r}
d1 = fromJSON("alts.json", simplifyDataFrame=T)
d1 = as.data.frame(d1)
# conver to lower case
sapply(seq(1, ncol(d1)), FUN=function(i) {
  d1[,i] = tolower(d1[,i])
})

sort(table(d1$all))
sort(table(d1$some))
sort(table(d1$unforgettable))
sort(table(d1$memorable))
sort(table(d1$excellent))
sort(table(d1$good))
sort(table(d1$loved))
sort(table(d1$liked))
sort(table(d1$delicious))
sort(table(d1$palatable))

>>>>

```{r}
rm(list = ls())
#library(rjson)
library(jsonlite)
fp = "~/Desktop/Projects/scalar_implicature/analysis/"
setwd("~/Desktop/Projects/scalar_implicature/")
```

**Analysis of alternative gathering experiment**

Data cleaning in alts_analysis.py

Explore
--------
```{r}
d1 = fromJSON("analysis/edited_alts.json", simplifyDataFrame=T)
d1 = as.data.frame(d1)

length(sort(table(d1$all)))
length(sort(table(d1$some)))

length(sort(table(d1$unforgettable)))
length(sort(table(d1$memorable)))

length(sort(table(d1$excellent)))
length(sort(table(d1$good)))

length(sort(table(d1$loved)))
length(sort(table(d1$liked)))

length(sort(table(d1$delicious)))
length(sort(table(d1$palatable)))
